Financial reports data  - comparison of sources

### 2020-08-21 auxilary_scripts/Finrep_data_comparison.Rmd
move comparison to separate script

----
title: Financial reports data  - comparison of sources
----

@@

>>>>

---
title: Financial reports data  - comparison of sources
---

```{r import_temp_data}

raw_data = read_rds(paste0(
  file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
  "\\OneDrive - Bank Of Israel\\Data\\TASE",
  " liquidity\\Current cache files\\raw_data.RDS"))

vars_status = read_csv(paste0(
  file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
  "\\OneDrive - Bank Of Israel\\Data\\TASE",
  " liquidity\\Variables_List.csv"))

\subsection{Financial reports}

This dataset has data on financial reports of TASE companies.
The data covers `r length(unique(raw_data$finrep_df$tase_id))` companies for the period `r paste0(range(raw_data$finrep_df$date), collapse = "-")` at quarterly frequency.

```{r summary_finrep_df, results='asis', eval=FALSE}

stargazer(raw_data$finrep_df %>% 
            select(-date_yearqtr,-tase_id) %>% 
            as.data.frame(),
          summary = TRUE, header = FALSE, digits = 2,
          summary.stat = c("n","mean","median","max","min"))

\subsection{Market data}
A dataset with market data (market capitalization, turnover) that allows to calculate Amihud's iiliquidity measure. The data time period is `r paste0(range(raw_data$market_df$date_yearqtr), collapse = "-")` at quarterly frequency.

```{r summary_market_df, results='asis', eval=FALSE}

stargazer(raw_data$market_df %>% 
            select(-sec_id,-date_yearqtr) %>% 
            as.data.frame(),
          summary = TRUE, header = FALSE, digits = 2)

\subsection{Nimrod's dataset}

```{r Import_nimrod_dataset}

raw_data$nimrod_stata_df = import.nimrod.stata.df(paste0(
  file.path(Sys.getenv("USERPROFILE"),fsep = "\\"),
  "\\OneDrive - Bank Of Israel\\Data\\",
  "TASE liquidity\\Stata files",
  "\\TASE panel.dta")
  )

stata_df = raw_data$nimrod_stata_df %>% 
  select(any_of(parameters_list$nimrod_vars))

A dataset that was gathered by Nimrod . The data covers `r length(unique(stata_df$tase_id))` companies for the period `r paste0(range(stata_df$date), collapse = "-")` at quarterly frequency. 
The data adresses several categories:

\begin{itemize}
  \item
  Financial Reports
  \item
  Market data
\end{itemize}

```{r summary_df_stata, results="asis", eval=FALSE}

stargazer(stata_df %>% 
            select(-starts_with("tase"),-date) %>% 
            as.data.frame(),
          summary = TRUE,
          header = FALSE,
          summary.stat = c("n","mean","median","max","min"))

```{r plot_NA, eval=FALSE}

stata_df %>% 
  slice_sample(n = 1000) %>% 
  group_by(date) %>% 
  mutate(across(everything(), ~is.na(.))) %>% 
  pivot_longer(-date) %>% 
  ggplot(aes(x = date, y = name, color = value)) + 
  scale_color_manual(values = c("TRUE" = "magenta", "FALSE" = "gray")) + 
  geom_point(show.legend = FALSE) + 
  theme_bw()

\subsubsection{Comparison of financial reports data}

@@

```{r diff_example}

inner_join(oracle_mos_diff_df %>% 
  filter(tase_id == 666) %>% 
  select(-diff),
  oracle_nimrod_diff_df %>% 
  filter(tase_id == 666) %>% 
  select(-diff)) %>% 
  filter(feature == "operating_profit") %>% 
  pivot_longer(oracle:nimrod,names_to = "source") %>% 
  ggplot(aes(x = date_yearqtr, y = value, color = source)) + 
  geom_line() + 
  xlab(NULL) + ylab(NULL) + ggtitle("Amos Luzon group operating profit") + 
  theme_bw() + 
  theme(legend.position = "bottom")
